Reproducible, flexible and high throughput data extraction from primary literature: The \pkg{metaDigitise} \proglang{R} package \vskip15pt Supplementary Materials

### 2018-03-07 docs/MEE_submission/manuscript_MEE.tex
Shinichi's changes

@@

% remove page numbers
\pagenumbering{gobble}

@@

In many different contexts, researchers make use of data presented in primary literature. Most notably, this includes meta-analysis, which is becoming increasingly common in many research fields. Meta-analysis uses effect size estimates and their sampling variance, taken from many studies, to understand whether particular effects are common across studies and to explain variation among these effects \citep{Glass1976,Borenstein2009,Koricheva2013,Naka2017}. Meta-analysis relies on descriptive statistics (e.g. means, standard deviations (SD), sample sizes, correlation coefficients) extracted from primary literature that have been reported in the text or tables of research papers. Descriptive statistics are also, however, frequently presented in figures and so need to be manually extracted using digitising programs. While inferential statistics (e.g., \textit{t}- and \textit{F}-statistics) are often presented along side descriptive statistics, and can be used to derive effect sizes, descriptive statistics are much more appropriate to use because sources of non-independence in experimental designs can be dealt with more easily \citep{Noble2017}.

@@

Data extraction from figures is therefore an incredibly time-consuming process as existing software does not provide an optimized research pipeline to facilitate data extraction and editing. Furthermore, although meta-analysis is an important tool in consolidating the data from multiple studies, many of the processes involved in data extraction are opaque and difficult to reproduce, making extending studies problematic. Having a tool that facilitates reproducibility in meta-analyses will increase transparency and aid in resolving the reproducibility crises seen in many fields \citep{peng_reproducible_2006, peng_reproducible_2011, sandve_ten_2013, Parker2016,Ihle2017}.

>>>>

% remove page numbers
%\pagenumbering{gobble}

@@

@@

In many different contexts, researchers make use of data presented in primary literature. Most notably, this includes meta-analysis, which is becoming increasingly common in many research fields. Meta-analysis uses effect size estimates and their sampling variance, taken from many studies, to understand whether particular effects are common across studies and to explain variation among these effects \citep{Glass1976,Koricheva2013,Naka2017}. Meta-analysis relies on descriptive statistics (e.g. means, standard deviations (SD), sample sizes, correlation coefficients) extracted from primary literature that have been reported in the text or tables of research papers. Descriptive statistics are also, however, frequently presented in figures and so need to be manually extracted using digitising programs. While inferential statistics (e.g., \textit{t}- and \textit{F}-statistics) are often presented along side descriptive statistics, and can be used to derive effect sizes, descriptive statistics are much more appropriate to use because sources of non-independence in experimental designs can be dealt with more easily \citep{Noble2017}.

@@

Data extraction from figures is therefore an incredibly time-consuming process as existing software does not provide an optimized research pipeline to facilitate data extraction and editing. Furthermore, although meta-analysis is an important tool in consolidating the data from multiple studies, many of the processes involved in data extraction are opaque and difficult to reproduce, making extending studies problematic. Having a tool that facilitates reproducibility in meta-analyses will increase transparency and aid in resolving the reproducibility crises seen in many fields \citep{peng_reproducible_2006, peng_reproducible_2011, Parker2016}.
